Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (4)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{resposta} 
Indeed, we did not inform the impact of changing the computer setup or related issues. We thank the reviewer for this observation. We have revised our manuscript to include the following paragraph in Section "5.2 Objectives and Setup": "Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the \textcolor{red}{coded problem (software created by authors) to be solved. Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results}.".
\end{resposta}

>>>>

\begin{resposta} 
Indeed, we did not inform the impact of changing the computer setup or related issues. We thank the reviewer for this observation. We have revised our manuscript to include the following paragraph in Section "5.2 Objectives and Setup": ``Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the implemented model (software created by the authors) to be solved. Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results.''.
\end{resposta}
